---
font.size = 10pt
---

### Appendix: Diagnostic Plots and R Code
*Audrey Chu*

```{r include = FALSE}
library(MASS)
library(car)
library(forecast)
library(astsa)
source('~/Documents/3rd Year/STA137/trndseas.R')
source('~/Documents/3rd Year/STA137/aicc.R')
```


##### Original Data
```{r, fig.align="center", fig.height=3, fig.width=6}
time = 1:384
y = read.table("~/Documents/3rd Year/STA137/EnergyConsumption.txt", row.names=NULL)[,3]
plot(time, y, type='l', main = "Figure 1
     U.S. Residential Sector Petroleum Consumption", ylab="Trillion BTU", xlab="Month and Year")
model = lm(y~time)
summary(model)
```
```{r, fig.width=4, fig.height=3, fig.align="center"}
plot(1:12, y[1:12], type='l', main="Figure 1.1
     Petroleum Consumption for 1984 Year", ylab="Trillion BTU", xlab="Months")
points(6, y[6], col='blue', pch=18)
points(10, y[10], col='blue', pch=18)
```

##### Box-Cox Transformation
<center> Figure 2.0 </center>
```{r, fig.align="center", fig.heigh=4, }
par(mfrow=c(2,2))
plot.ts(y^(-1),ylab=expression(paste("1/",Y[t],")")), main=expression(paste("1/(",Y[t],")")))
plot.ts(y^.5,ylab=expression(paste("sqrt(",Y[t],")")), main=expression(paste("Plot of Sqrt(",Y[t],")")))
plot.ts(y^-.5,ylab=expression(paste("1/sqrt(",Y[t],")")), main=expression(paste("Plot of 1/sqrt(",Y[t],")")))
plot.ts(log(y),ylab=expression(paste("ln(",Y[t],")")), main=expression(paste("Plot of ln(",Y[t],")"))) 
```

<center> Figure 2.1 </center>
```{r, fig.align="center", fig.height=3}
par(mfrow=c(1,2))
boxcox(model)
powerTransform(model)
ytrans = y^(-1)
modtrans = lm(ytrans~time)
plot(time, ytrans, type = 'l', main = "Transformed Petroleum")
```

##### Trend and Seasonal Estimation
<center> Figure 3.0 </center>
```{r, fig.align="center", fig.heigh=4, fig.width=6}
mod = trndseas(ytrans,degtrnd=2, seas=12)
mod$rsq
mod$lamopt
m.fit = mod$trend
s.fit = rep(mod$season,length.out=384)
par(mfrow=c(2,2))
plot.ts(ytrans ,ylab=expression(paste("",Ytrans[t],"")), main=expression(paste("Plot of ",Ytrans[t],"")))
plot.ts(m.fit, ylab=expression(paste("",Ytrans[t],"")), main=expression(paste("Estimated Trend (",m[t],")")))
plot.ts(s.fit,main=expression(paste("Estimated Seasonal Component (",s[t],")")))
plot.ts(ytrans,ylab=expression(paste("",Ytrans[t],"")), main=expression(paste("",Ytrans[t]," with Seasonality and Trend")))
points(mod$fit,type='l',col='red')
mod$coef
```

##### Rough Estimation
<center> Figure 4.0 </center>
```{r, fig.align="center", fig.heigh=4, fig.width=6}
x = ytrans - m.fit - s.fit
par(mfrow=c(2,2))
acf(x, main= "ACF Plot of Resid", ylab = "ACF", xlab ="Lag")
pacf(x, main= "PACF Plot of Resid", ylab = "PACF", xlab = "Lag")
hist(x, main= "Histogram of Resid", ylab = "Frequency", xlab = "Residual")
qqnorm(x, main= "Normal Prob Plot of Resid",ylab="Residual"); qqline(x)
```
```{r, fig.width=4, fig.height=3, fig.align="center"}
par(mfrow=c(1,1))
plot.ts(x, main = "Figure 4.1
        Plot of Residuals", ylab = "")
Box.test(x,lag=10,'Ljung-Box')
```

Box-Ljung test shows a very low p-value, which can be
intepreted as significant.  This means that the rough series is not
independent.

```{r, fig.width=4, fig.height=3, fig.align="center"}
xpgrm = spec.pgram(x,log='no',plot=F)
plot(xpgrm$freq,xpgrm$spec,type='l',xlab='Frequency',ylab='', main = 'Figure 5.0
    Raw Periodogram')
xpgrm5 = spec.pgram(x,spans=5, main = "Figure 5.1
    Smoothed Periodogram (5 Month)")
xpgrm7 = spec.pgram(x,spans=7, main="Figure 5.2
    Smoothed Periodogram (7 Month)")
xpgrm9 = spec.pgram(x,spans=9, main="Figure 5.3
    Smoothed Periodogram (11 Month)")
xpgrm11 = spec.pgram(x,spans=11, main="Figure 5.4
    Smoothed Periodogram (11 Month)")
```


##### Preliminary ARMA(p, q) or ARIMA(p, d, q) Model
```{r, fig.width=4, fig.height=3, fig.align="center"}
fitARMA0 = arima(x, order=c(0,0,0))
fitARMA14 = arima(x, order=c(1,0,4))
fitARMA24 = arima(x, order=c(2,0,4))
fitARMA34 = arima(x, order=c(3,0,4))
fitARMA44 = arima(x, order=c(4,0,4))
fitARMA54 = arima(x, order=c(5,0,4))
fitARMA45 = arima(x, order=c(4,0,5))
aicc(fitARMA0)
aicc(fitARMA14)
aicc(fitARMA24)
aicc(fitARMA34)
aicc(fitARMA44)
aicc(fitARMA54)
aicc(fitARMA45)
auto = auto.arima(x, max.p = 8, max.q =8, max.d = 2); auto
fitARIMA405 = arima(x, order=c(4, 0, 5))
aicc(fitARIMA405)
```
```{r, fig.align="center", fig.height=3, fig.width=6}
par(mfrow=c(1,1))
res = fitARIMA405$res
ts.plot(res, main = "Figure 6.0
  Plot of Residual of ARIMA(4,0,5)")
h=12
n = 372
fcast = predict(fitARIMA405,n.ahead=h)
fc = fcast$pred
upper = fc+qnorm(0.975)*fcast$se
lower = fc-qnorm(0.975)*fcast$se
polygon(x=c(n+1:h,n+h:1),y=c(upper,rev(lower)),col='lightblue',border=NA)
lines(x=n+(1:h),y=fc,col='blue')
```


<center> Figure 7.0 </center>
```{r, fig.align="center", fig.height=3}
par(mfrow=c(1,2))
acf(res, main = "ACF of ARIMA(4,0,5) Residual")
pacf(res, main = "PACF of ARIMA(4,0,5) Residual")
```

<center> Figure 7.1 </center>
```{r, fig.align="center", fig.height=3}
par(mfrow=c(1,2))
hist(res, main = "Histogram of Residual")
qqnorm(res); qqline(res)
```

```{r, fig.align="center", fig.height=3, fig.width=6}
par(mfrow=c(1,1))
boxplot(res, main = "Figure 7.2
        Boxplot of Residuals")
Box.test(res,lag=10,'Ljung-Box')
```

##### Spectral Density
```{r, fig.align="center", fig.heigh=4, fig.width=6}
coef.ar = auto$coef[1:4]
coef.ma = auto$coef[5:9]
sigma2 = auto$sigma2
```
```{r, include=FALSE}
mod1spec = arma.spec(ar=coef.ar,ma=coef.ma,var.noise=sigma2,log='no', main="ARMA(4,5) Spectrum and Smoothed Periodogram (7 month)", xlim=c(0,.2))
```
```{r, fig.align="center", fig.height=3, fig.width=6}
mod1spec = arma.spec(ar=coef.ar, ma=coef.ma, var.noise=sigma2, log='no', main="Figure 8.0
ARMA(4,5) Spectrum & Smoothed Periodogram (7 Month)", xlim=c(0.0,0.3), ylab="Spectrum", xlab="Frequency", ylim=c(0,15.0e-09))
points(xpgrm7$freq, xpgrm7$spec, type='l', col='blue')
legend(0.15, 13.0e-09, c("Smoothed", "Spectral Density"), lty=c(1,1), col=c('blue', 'black'))
```

##### Prediction
```{r, fig.align="center", fig.height=4, fig.width=6}
# Prediction of time 372 to 384
y372 = y[1:372]
n = 372
h=12
# Forecast the trend
deg = 2
coef = mod$coef[1:(deg+1)]
time = (n+(1:h))/n; time
predmat = matrix(rep(time,deg)^rep(1:deg,each=h),nrow=h,byrow=F)
predmat = cbind(rep(1,h),predmat); predmat
m.fc = predmat %*% coef
# Forecast the seasonality
s.fc = rep(mod$season,length.out=n+h)
s.fc = s.fc[-(1:n)]
# Forecast the rough part
fcast = predict(fitARIMA405,n.ahead=h)
x.fc = fcast$pred
# Combine forecasts
y.fc = ( m.fc + s.fc + x.fc)^(-1)
y.fc
par(mfrow=c(1,1))
oldy=y[1:372]
plot.ts(oldy,xlim=c(0,n+h), main = "Figure 9.0
Petroleum Prediction from December 2014", ylab= "Trillion BTU", pch=1)
points(x=n+1:h, y=y.fc, col='blue',type='l',pch=8)
legend(0, 2800, c("Forecasted 2015"), lty=c(1,1), col=c('blue'))
```
